My title

### 2024-04-21 paper/paper.qmd
im so tired. also i am trying to use s&p 500 and parquet but it WONT WORK

library(tidyverse)
library(tinytex)
library(kableExtra)
library(knitr)
library(janitor)
library(kableExtra)
library(ggplot2)
library(xts)

@@

cleaned_data_SBUX <- read.csv("../data/analysis_data/cleaned_data_SBUX.csv")
cleaned_data_SBUX <- 
  cleaned_data_SBUX |>
  mutate(Date = lubridate::ymd(Date))
cleaned_data_SBUX$Date <- 
  as.Date(cleaned_data_SBUX$Date, format='%Y-%m-%d')
```

@@

>>>>

library(tidyverse)
library(tinytex)
library(kableExtra)
library(knitr)
library(janitor)
library(kableExtra)
library(ggplot2)
library(xts)
library(tidyquant)

@@

cleaned_data_SBUX <- read.csv("../data/analysis_data/cleaned_data_SBUX.csv")
cleaned_data_SBUX <- 
  cleaned_data_SBUX |>
  mutate(Date = lubridate::ymd(Date))
cleaned_data_SBUX$Date <- 
  as.Date(cleaned_data_SBUX$Date, format='%Y-%m-%d')

raw_data_SPX <- tq_get('SPX',
               from = "1991-07-12",
               to = "2023-03-29",
               get = "stock.prices")

@@

```{r}
SBUX_SPX <-
  cleaned_data_SPX |>
  filter(between(date, as.Date('2023-10-18'), as.Date('2023-11-06')))

class(cleaned_data_SPX$date)

matplot(cleaned_data_SBUX, cbind(cleaned_data_SBUX$Close, cleaned_data_SPX$close), type = "l", lty = 1, 
        col = c("red", "blue"), xlab = "X", 
        ylab = "Y", main = "Multiple Lines Plot")
legend("topright", legend = c("Line 1", "Line 2"), 
       col = c("red", "blue"), 
       lty = 1)
```
